Figure 3 - ChIP

### 2024-07-09 ms_figure_3_chip.Rmd
remove IP-MS HOT TF heatmap from figure 3

---
title: "Figure 3 - ChIP"
author: "Michael Stadler, Charlotte Soneson, Merle Skribbe"
date: "`r Sys.Date()`"
output: 
    html_document:
        theme: united
        toc: true
        toc_float: true
        code_folding: hide
params:
    genomefasta: "reference/Schizosaccharomyces_pombe.ASM294v2.dna.toplevel.fa"
    gtf: "reference/Schizosaccharomyces_pombe.ASM294v2.55.gtf"
    chiptrackfile: "data/genome_browser_tracks_chipseq.csv.gz"
    peakcsv: "data/fused_peaks_filtered.csv.gz"
    peakenr: "data/fused_peaks_filtered_enrichments.csv.gz"
    peakchipfile: "data/fused_peaks_filtered_counts-external_chip.csv.gz"
    dbdtxt: "data/TF_DBD_annotation.txt"
    motifrds: "data/motifs_annotated.rds"
    txcsv: "data/promoters-1kb_tes-1kb_annotated.csv.gz"
    ipms150untag: "data/ipms_150_untag_sce.rds"
editor_options: 
    chunk_output_type: console
---

@@

source("params/plot_settings.R")
source("params/get_testres_function.R")
source("params/mapping_functions.R")
source("params/plottracks_function.R")

@@

## IP-MS data for HOT TFs

```{r ipms-hot}
#| fig.width: 9
#| fig.height: 9

sce150untag <- readRDS(params$ipms150untag)

res150untag <- .getTestCols(sce150untag, adjp_cutoff = 0.01, logfc_cutoff = 1)
tstat <- res150untag$tstat
colnames(tstat) <- .getProteinNameFromComparison(colnames(tstat))
tstat <- tstat[rownames(tstat) %in% colnames(tstat), ]
tstat[is.na(tstat)] <- 0
dim(tstat)

hot_tfs <- c("Php3", "Sak1", "Pcr1", "Prr1", "Atf1", "Rst2", "Adn2", 
             "Adn3", "Hsr1", "Phx1", "Pho7")
stopifnot(all(hot_tfs %in% rownames(tstat)))
stopifnot(all(hot_tfs %in% colnames(tstat)))
stopifnot(all(rownames(tstat) %in% colnames(tstat)))
tstat <- tstat[c(hot_tfs, setdiff(rownames(tstat), hot_tfs)), ]
tstat <- tstat[, c(rownames(tstat), setdiff(colnames(tstat), rownames(tstat)))]

hmipmshot <- Heatmap(
    tstat, 
    col = circlize::colorRamp2(
        breaks = seq(3.0, 13.0, length.out = 64),
        colors = colorRampPalette(binary_heatmap_colors[c("FALSE", "TRUE")])(64)),
    border = TRUE,
    row_split = ifelse(rownames(tstat) %in% hot_tfs, "HOT TFs", "Other TFs"), 
    column_split = ifelse(colnames(tstat) %in% hot_tfs, "HOT TFs", "Other TFs"),
    cluster_rows = FALSE, cluster_columns = FALSE,
    row_title_gp = gpar(fontsize = fl), row_names_gp = gpar(fontsize = fs),
    column_title_gp = gpar(fontsize = fl), show_column_names = FALSE,
    heatmap_legend_param = list(labels_gp = gpar(fontsize = fs),
                                border = "gray10",
                                legend_direction = "horizontal",
                                legend_width = unit(24, "mm"),
                                title_position = "lefttop",
                                title_gp = gpar(fontsize = fl)),
    na_col = bg_color,
    name = "Mod. t-stat.")

hm_ipms_hot <- grid.grabExpr(
    hmipmshot <- draw(hmipmshot, merge_legend = TRUE, 
                      heatmap_legend_side = "bottom")
)
plot_grid(hm_ipms_hot)
```

>>>>

---
title: "Figure 3 - ChIP"
author: "Michael Stadler, Charlotte Soneson, Merle Skribbe"
date: "`r Sys.Date()`"
output: 
    html_document:
        theme: united
        toc: true
        toc_float: true
        code_folding: hide
params:
    genomefasta: "reference/Schizosaccharomyces_pombe.ASM294v2.dna.toplevel.fa"
    gtf: "reference/Schizosaccharomyces_pombe.ASM294v2.55.gtf"
    chiptrackfile: "data/genome_browser_tracks_chipseq.csv.gz"
    peakcsv: "data/fused_peaks_filtered.csv.gz"
    peakenr: "data/fused_peaks_filtered_enrichments.csv.gz"
    peakchipfile: "data/fused_peaks_filtered_counts-external_chip.csv.gz"
    dbdtxt: "data/TF_DBD_annotation.txt"
    motifrds: "data/motifs_annotated.rds"
    txcsv: "data/promoters-1kb_tes-1kb_annotated.csv.gz"
editor_options: 
    chunk_output_type: console
---

@@

source("params/plot_settings.R")
source("params/plottracks_function.R")

@@

```
